A Large-Scale 3D Object Recognition dataset

### 2016-07-13 paper.tex
almost finish

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a new large scale dataset suited for evaluation of local shape descriptors and 3d object recognition algorithms. The dataset consists of 3200 scenes and 45 different 3D object models. The individual scenes contain 10 occluded objects where the objects belongs to different geometric groups; concave, convex, cylindrical and flat 3D object models. The object models have varying amount of local geometric features to challenge existing local shape feature descriptors in terms of descriptiveness and robustness. The dataset is validated in a benchmark which evaluates the matching performance of 7 different state-of-the-art local shape descriptors. Further, we validate the dataset in a 3D object recognition pipeline. Our benchmark shows as expected that local shape feature descriptors without any global point relation across the surface have a poor matching performance with flat and cylindrical objects. It is our objective that this dataset contributes to the future development of next generation of 3D object recognition algorithms. The dataset will be made public available.
\end{abstract}

@@

%%%%%%%%%%Page limits = 8 exclusive references
%Intro and related work -> 2.5 page
%Experiantal design -> 1 page
%Benchmark -> 1 page
%Evaluation/results -> 3 pages
% conclusion/discussion -> 1/2 page
\section{Introduction} %Hvad, hvorfor, hvordan
Object recognition in range images is a fundamental research area in computer vision with many different applications in different industries. With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology in the future. Applications areas such as robotic assembly, bin-picking, mobile robotic manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for localizing objects. Mainly, because the third dimension is explicit given and not inferred as in 2D object pose estimation. In the last decades many contributions on 2D object recognition and classification have been published, where methods are evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014} and ImageNet \cite{Imagenet2009}. The benefit from evaluating algorithms on a large-scale dataset has proven valuable in the continues improvement of recognition algorithms after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.
\begin{figure}[t]
\centering
\includegraphics[clip, trim=14cm 5cm 10cm 5cm,width=0.8\linewidth, height= 0.8\linewidth, keepaspectratio]{img/scenes/full_scene00.png}
\caption{Example of a full registered scene included in the dataset}
\label{fig:scene}
\end{figure}
In 3D object recognition research, large-scale datasets that consist of a set of 3D querie models $Q_n$, 3D target scenes $S_t$ and ground truth poses $T_{gt}$ for each object in each scene are required in order to be able to evaluate existing and future 3D object recognition algorithms better. Until now, 3D object recognition algorithms are evaluated with eight smaller datasets \cite{Guo2015}, including in the UWA \cite{Mian2006},\cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2007} and Bologna \cite{Salti2014},\cite{Tombari2010} datasets. Other, smaller dataset like the Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2\cite{Lai2011}, \cite{Lai2014} are proposed. Common for all datasets is that the amount of scenes and/or models are limited.\\

In this paper we present a new large-scale dataset consisting of 45 objects and 3200 scenes. The new dataset is recorded systematically in an environment without ambient light and with controlled illumination. The system includes an industrial robot in a dark chamber, a high precision structured light scanner which records data of 292 different scenes from 11 different view points. Each scene consists of 10 occluded objects, automatic taken with the structured light sensor, which results in a dataset with around 32000 unique object poses. With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition. The objects are configured as a classic table-top scenario where different objects are depicted for the side. The dataset is not meant as an evaluation platform for bin-picking and top-view scenarios where many instances of the same object are present in the scene. The table-top scenario is selected because it encapsulate many of the problems and challenges in 3D object recognition in favour of a larger research community.
Our 45 object models are scanned in a similar dark chamber with a high precision structured light scanner and a rotation table. With this setup we are able to scan objects with an average point resolution of 275 microns. We validate our dataset by evaluating state of the art local shape features in a 3D object recognition pipeline.\\ %In Table \ref{tab:datasets} a summery of the features of ours and state of the art dataset are presented.\\
\textit{Why does the 3D Object recognition community need another dataset?} Previous proposed datasets are limited in the total number of objects, object per. scene and total number of scenes. Additional, the included objects in the different datasets are mostly geometrical ideal objects. With geometrical ideal objects we refers to objects with concave water tight and closed surfaces that are rich of natural local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}. In our dataset we include not only ideal concave objects, but flat, cylindrical, feature-rich, simple concave and convex objects. It is expected that some local shape features will have a poor performance on our dataset because the lack of local geometric features. However, our main goal for proposing this dataset is to strengthen the focus on the challenges in 3D object recognition research and future algorithm development. This work is initiated because of previous experiences on pose estimation of geometric simple objects in an industrial robotic context. We hope that new novel methods for 3D object recognition will emerge in the future as a side-effect of this dataset. Not only local shape descriptos but to a great extend features that uses point relations across the surface e.g. Point Pair Features \cite{BirdalIlic2015}, semi-global features and template matching.

Our objects are a combination of lab-objects and industrial objects, selected from companies that want to pick these objects from boxes or bins with a robot.\\
This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented. Section \ref{sec:exp_design} outlines our experimental design followed by Section \ref{sec:benchmark} which presents our benchmarking methodology. In Section \ref{sec:evaluation} the results are given followed by a discussion and conclusion in Section \ref{sec:conclusion}. 

@@

\label{tab:datasets}

@@

@@

\caption{Comparison of existing datasets for 3D object recognition with the presented datasets. {$M_q$} is the amount of different models in the dataset and {$S_t$} is the amount of scenes.[R]/[S] indicates whether the dataset is synthetic or acquired in real world. }
\end{table*}
%\end{multicols}
%-------------------------------------------------------------------------
\section{Related work}\label{sec:related_work}
%We are not considering learning approaches
\noindent
\textbf{3D Object Recognition datasets:}\\
The last 10 years a few 3D object recognition datasets have been published. Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}. Common for all existing dataset are the limited number of 3D object models and scenes. A comparison of the different datasets are presented in Table \ref{tab:dataset_overview}. The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}. These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}. The main problems of all the datasets are; size, variety of objects and occlusion/clutter estimates. The recent comparison studies \cite{Buch2016},\cite{Guo2015} revival that the data for evaluation is not good enough to scientific distinguish results. The studies showed that the performance of one local feature descriptor is poor when evaluated on one dataset but fail in other datasets. These results reveal that a larger data foundation is required in the quest to find shape features which generalize over many object categories.\\

\noindent
\textbf{Local feature descriptors:}\\
During the last three decades, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Context (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensors \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH) \cite{Rusu2008}, Fast Point Feature Histograms (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and Tri-Spin-Image (TriSI)\cite{Guo2015}. The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others. Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic. Recent studies have shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}. The studies proved one of the main issues in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g. flat, rotational symmetrical and geometrically feature rich objects. What feature(s) to use are still dependent on the object geometry. These studies pose a relevant research question; are the local feature descriptors not descriptive enough to generalize over different object classes or are the data used for evaluation too limited? The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.\\ 
Local feature descriptors aim at computing a distinctive and robust N-dimensional feature vector around a point, by considering the points in an Euclidean neighbourhood. The support radius determining the size of the neighbourhood is often one of the critical parameters in the pipeline. Local feature descriptors are often split into two different categories, spatial and geometrical histograms \cite{Salti2014}. %Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry. {\color{blue} TS I would remove the last sentence about global descriptors.}

%and pose estimation \cite{Viksten09}, \cite{Hinterstoisser2012}, this kind of scientific validations of results still lacks in 3D object recognition. 
%2D object recognition is well studied lacking with 3D. Keypoint comparison Aan{\ae}s et.al. \cite{Aanaes2011}

%We study the performance of the top six local shape features and one global descriptor 
%Limitations in current dataset and algorithms. Feature rich objects not flat or cylindrical objects

@@

\subsection{Object model scanning}

@@

a high resolution DLP projector (LG PF80G) mounted on a rigid aluminium frame. In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object. Each of the 45 objects are incremental scanned with a rotation of 20 degrees. All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000} which results in accurate and dense point cloud of the objects. Eleven temporal binary gray code patterns are projected followed by eight line shifting patterns. The point resolution of the scanned objects are in average 275 microns and consist of around 908000 vertices and 1.8 million faces in average. Once a single view of the model is scanned, noisy outliers of the measurement are manual removed and surface normals are estimated to ensure consistent normals. All 18 views are registered with Iterative Closest Point (ICP) and a new object frame is computed with principal component analysis on the point set.
All models are sampled with a Poisson disk sampling algorithm \cite{Corsini2012} and triangulated with the poisson reconstruction algorithm \cite{Kazhdan2006} with an octree depth=14, solver divide = 8 and iso divide = 5. We use the PCL implementation \cite{RusuCousins2011}. All models are provided as coloured point clouds and triangular meshes, all in the $.ply$ format, see Figure \ref{fig:objects}. Note that the modelling setup is not radiometrical calibrated.

@@

\includegraphics[width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/objects/objects.pdf}
\caption{Four of the fifty scanned and triangulated object models}

@@

@@

\subsection{Scene scanning} 
For the data collection we use a 6-axis ABB IRB 1600 industrial robot to provide a precise and highly repeatable camera pose. The robot is depicted in Figure \ref{fig:robot}. The robot is equipped with two PointGray Grasshopper3 GS3-U391S6C-C USB3 color cameras with resolution of 9.1 Mp and a Wintech Pro4500 projector with a resolution of 1140x912 pixels. The sensor cluster with the structured light sensor (SL) is mounted in the robot tool. 

@@

\includegraphics[width=1.0\linewidth, height= 0.7\linewidth]{Robot.pdf}
\caption{Scan of the full scene with view frames}
\label{fig:robot}

@@

\includegraphics[clip, trim=12cm 6cm 12cm 8cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/mesh_scene.png}

@@

\subsection{Ground Truth 6D pose}

@@

\subsection{Pose estimation}

@@

In this section we present the results of our evaluation benchmark. All tests are based on the proposed dataset where 3204 scenes, 45 objects and 5675 ground truth poses are included. As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models are included. The PRC curve of the overall matching accuracy is presented in Figure \ref{fig:all_L2_RATIO_zoom}.   

@@

As expected the total matching accuracy is much lower compared to previous studies e.g. Guo \etal \cite{Guo2015} and Buch \etal \cite{Buch2016}, which both are running a similar benchmark but on previous proposed datasets. The result indicate that our objective of the proposed dataset has been fulfilled. Moreover, the evaluation shows that the ECSAD feature has a best performance with a AUC = 0.046 followed by ROPS with AUC = 0.011. In order to investigate the performance further we run the matching benchmark for each quire and compute PRC curves for each of the 45 models. We have categorize the object into three different groups and present 3 PRC curves for each group in Figure \ref{fig:angel}-\ref{fig:noise} as a sample. The three groups are a) Geometric complex objects, b) Cylindrical objects and c) Flat or box shaped objects. The objects that corresponds to the PRC curves in Figure \ref{fig:angel}-\ref{fig:noise} are presented in Figure \ref{fig:selected_objects}. The geometric complex objects are the Angel, the Birds and the Rabbit in Figure \ref{fig:selected_objects}(a)-(c), the cylindrical objects are Neutral, Pringles and Hand soap in Figure \ref{fig:selected_objects}(d)-(f), and the flat or box shaped objects are the button, the brake disc and the Psu in Figure \ref{fig:selected_objects}(g)-(i). These PRC curves

%As expected we see that all local shape feature in this benchmark have a hard time to establish correct matches 
%Object recognition:
%We first one run with a single query model. This is the hardest problem because we segment point belonging to a detected object away from the target. Thus, with more instances the individal matches are segmented first and therefor boost the probability for correct matches for the next object because objects beloning to the first object is remove from the target mesh.

%"In general the matching accuracy of a descriptor is expected to increase with increasing support radius, except in cases where occlusion and clutter are present."

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a new large scale dataset targeting evaluation of local shape descriptors and 3d object recognition algorithms. The dataset consists of point clouds and triangulated meshes from 292 physical scenes take from 11 different views; a total of approximately 3200 views. Each of the physical scenes contain 10 occluded objects resulting in a dataset with around 32000 unique object poses and 45 different object models. The 45 object models are full 360 degree models which are scanned with a high precision structured light scanner and a turntable. All the included objects belongs to different geometric groups; concave, convex, cylindrical and flat 3D object models. The object models have varying amount of local geometric features to challenge existing local shape feature descriptors in terms of descriptiveness and robustness.  The dataset is validated in a benchmark which evaluates the matching performance of 7 different state-of-the-art local shape descriptors. Further, we validate the dataset in a 3D object recognition pipeline. Our benchmark shows as expected that local shape feature descriptors without any global point relation across the surface have a poor matching performance with flat and cylindrical objects. It is our objective that this dataset contributes to the future development of next generation of 3D object recognition algorithms. The dataset will be made public available.
\end{abstract}

@@

%%%%%%%%%%Page limits = 8 exclusive references
%Intro and related work -> 2.5 page
%Experiantal design -> 1 page
%Benchmark -> 1 page
%Evaluation/results -> 3 pages
% conclusion/discussion -> 1/2 page
\section{Introduction} %Hvad, hvorfor, hvordan
Object recognition in range images is a fundamental research area in computer vision with many different applications in different industries. With the continually introduction of new inexpensive 3D sensors for different applications, the ability to localize and recognize rigid and no rigid objects is an attractive and unavoidable technology. Applications areas such as robotic assembly, bin-picking, mobile robotic manipulation, biometric analysis, tracking and intelligent surveillance all benefits from 3D data for localizing objects. Mainly, because the third dimension is explicit given and not inferred as in 2D object pose estimation. In the last decades many contributions on 2D object recognition and classification have been published, where methods are evaluated on large-scale dataset like the PASCAL Visual Object Challenge (VOC) \cite{Everingham2014} and ImageNet \cite{Imagenet2009}. The benefit from evaluating algorithms on a large-scale dataset has proven valuable in the continues improvement of recognition algorithms after the release of the PASCAL VOC and ImageNet datasets \cite{Everingham2014}.
\begin{figure}[t]
\includegraphics[clip, trim=14cm 5cm 10cm 5cm,width=0.8\linewidth, height= 0.8\linewidth, keepaspectratio]{img/scenes/full_scene00.png}
\caption{Example of a full registered scene included in the dataset}
\label{fig:scene}
In 3D object recognition research, large-scale datasets that consist of a set of 3D querie models $Q_n$, 3D target scenes $S_t$ and ground truth poses $T_{gt}$ for each object in each scene are required in order to be able to evaluate existing and future 3D object recognition algorithms better. Until now, 3D object recognition algorithms are evaluated with eight smaller datasets \cite{Guo2015}, including in the UWA \cite{Mian2006},\cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2007} and Bologna \cite{Salti2014},\cite{Tombari2010} datasets. Other, smaller dataset like the Vienna Kinect\cite{Aldoma2012}, TUM \cite{Rodola2013}, TUM-LineMod\cite{Hinterstoisser2012}, BigBird\cite{BigBIRD} and RGB-D dataset version 1 \& 2 \cite{Lai2011},\cite{Lai2014} are proposed. Common for all datasets is that the amount of scenes and/or models are limited.\\
\indent In this paper we present a new large-scale dataset consisting of 45 objects and 3200 views. The new dataset is recorded systematically in an environment without ambient light and with controlled illumination. The system includes an industrial robot in a dark chamber, a high precision structured light scanner which records data of 292 different scenes from 11 different view points. Each scene consists of 10 occluded objects, automatic taken with the structured light sensor, which results in a dataset with around 32000 unique object poses. With 11 different views of the same scene our dataset is especially suited for studying the effect of view point changes in 3D object recognition. The objects are configured as a classic table-top scenario where different objects are depicted for the side. The dataset is not meant as an evaluation platform for bin-picking and top-view scenarios where many instances of the same object are present in the scene. The table-top scenario is selected because it encapsulate many of the problems and challenges in 3D object recognition in favour of a larger research community.
Our 45 object models are scanned in a similar dark chamber with a high precision structured light scanner and a rotation table. With this setup we are able to scan objects with an average point resolution of 275 microns. We validate our dataset by evaluating state of the art local shape features in a 3D object recognition pipeline.\\ 
\indent \textit{Why does the 3D Object recognition community need another dataset?} Previous proposed datasets are limited in the total number of objects, object per. scene and total number of scenes. Additional, the included objects in the different datasets are mostly geometrical ideal objects. With geometrical ideal objects we refers to objects with concave water tight and closed surfaces that are rich of local descriptive geometrical features, like the UWA-chef model \cite{Mian2006},\cite{Mian2010}, the bologna-Armadillo \cite{Salti2014},\cite{Tombari2010} and the Queens-BigBird \cite{Taati2007},\cite{Taati2007}. In our dataset we include not only ideal concave objects, but flat, cylindrical, feature-rich, simple concave and convex objects. It is expected that some local shape features will have a poor performance on our dataset because the lack of local geometric features. However, our main goal for proposing this dataset is to highlight the challenges in 3D object recognition research and strengthen the data foundation in future algorithm development. This work is initiated because of previous experiences on pose estimation of geometric simple objects in an industrial robotic context. We hope that new novel methods for 3D object recognition will emerge in the future as a side-effect of this dataset. Not only local shape descriptos but to a great extend features that uses point relations across the surface e.g. Point Pair Features \cite{BirdalIlic2015}, semi-global features and template matching.    
We have selected the different objects based on previous experience, as a combination of lab-objects and industrial objects. The industrial objects are provided by companies that wish to pick the objects from boxes or bins with a robot. Thus, the dataset is a mix of objects that we know is problematic and objects from our lab which are more suited for in a 3D object recognition pipeline with local shape features.\\
\indent This paper is structured as follows: In Section \ref{sec:related_work} related datasets and local feature descriptors are presented. Section \ref{sec:exp_design} outlines our experimental design followed by Section \ref{sec:benchmark} which presents our benchmarking methodology. In Section \ref{sec:evaluation} the results are given followed by a discussion and conclusion in Section \ref{sec:conclusion}. 

@@

@@

\caption{Comparison of existing datasets for 3D object recognition with the presented datasets. {$M_q$} is the amount of different models in the dataset and {$S_t$} is the amount of scenes.[R]/[S] indicates whether the dataset is synthetic or acquired in real world. }

@@

\end{table*}
%\end{multicols}
\section{Related work}\label{sec:related_work}
%We are not considering learning approaches
We will now relate our work to state of the art. First, we review existing 3D object recognition datasets followed by a concise review of significant local feature descriptors.\\

\noindent
\textbf{3D Object Recognition datasets:}\\
The last 10 years a few 3D object recognition datasets have been published. Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}. Common for all existing dataset are the limited number of 3D object models and scenes. A comparison of the different datasets are presented in Table \ref{tab:dataset_overview}. The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}. These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}. The main problems of all the datasets are; size, variety of objects, few objects per. scene and missing occlusion/clutter estimates. For object recognition in 2.5D, where either a full object model or sampled templates are used for recognizing object in a color and depth image, is not considered in this work. However, some datasets exist for this problem e.g. the Line-Mod dataset \cite{Hinterstoisser2012}.\\

\noindent
\textbf{Local feature descriptors:}\\
During the last three decades, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Context (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensors \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH) \cite{Rusu2008}, Fast Point Feature Histograms (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and Tri-Spin-Image (TriSI)\cite{Guo2015}. The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others. Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic.

\indent Local feature descriptors aim at computing a distinctive and robust N-dimensional feature vector around a point, by considering the points in an Euclidean neighbourhood. The support radius determining the size of the neighbourhood is often one of the critical parameters in the pipeline. Local feature descriptors are often split into two different categories, spatial and geometrical histograms \cite{Salti2014}.
Recent studies have shown that the state of the art features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}. The studies proved one of the main issues in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g. flat, rotational symmetrical and geometrically feature rich objects. What feature(s) to use are still dependent on the object geometry. However, the experimental result in \cite{Buch2016} showed the advantage of fusing several local feature descriptors. 
The studies from \cite{Guo2015},\cite{Buch2016} leave a relevant research question to be answered; are the local feature descriptors not descriptive enough to generalize over different object classes or are the data used for evaluation too limited? The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features.\\ 
%The recent comparison studies \cite{Buch2016},\cite{Guo2015} revival that the data for evaluation is not good enough to scientific distinguish results. The studies showed that the performance of one local feature descriptor is poor when evaluated on one dataset but fail in other datasets. These results reveal that a larger data foundation is required in the quest to find shape features which generalize over many object categories.\\ 

@@

We have constructed a dataset by achieving highly accurate 3D model of each of the 45 individual objects, as described in Section \ref{sec:object_scanning}. These are then used to compose 292 individual scenes where 10 objects are placed in different configurations. A robot moves our scanner to 11 fixed positions in order to create 11 independent view points of the same object configuration, as described in Section \ref{sec:scene_scanning}. Hence, we have 3200 individual observations of 10 objects included in the dataset. We argue that these observations are independent because of the large view point change at 36 degree horizontal and 45 degree vertical. Thus, the objects surface are very different in each view. We achieve very accurate ground truth poses by annotating the entire dataset with our high resolution object models in full resolution, as described in Section \ref{sec:gt_pose}. 
\subsection{Object model scanning}\label{sec:object_scanning}

@@

a high resolution DLP projector (LG PF80G) mounted on a rigid aluminium frame. In addition, a high precision turntable (Newmark Systems RT-5) is used in order to provide automatic rotation of the object. Each of the 45 objects are incremental scanned with a rotation of 20 degrees. 
\begin{figure}[htp]

@@

\includegraphics[clip, trim=1cm 1cm 1cm 1.3cm,width=0.9\linewidth, height= 0.4\linewidth, keepaspectratio]{img/objects/objects.pdf}
\caption{A sample of the scanned object models}

@@

All individual scan views are reconstructed by the Line shifting algorithm \cite{Guehring2000} which results in accurate and dense point cloud of the objects. Eleven temporal binary gray code patterns are projected followed by eight line shifting patterns. The point resolution of the scanned objects are in average 275 microns and consist of around 908000 vertices and 1.8 million faces in average. Once a single view of the model is scanned, noisy outliers of the measurement are manual removed and surface normals are estimated to ensure consistent normals. All 18 views are registered with Iterative Closest Point (ICP) and a new object frame is computed with principal component analysis on the point set. All models are sampled with a Poisson disk sampling algorithm \cite{Corsini2012} and triangulated with the poisson reconstruction algorithm \cite{Kazhdan2006} with an octree depth=14, solver divide = 8 and iso divide = 5. We use the PCL implementation \cite{RusuCousins2011}. All models are provided as coloured point clouds and triangular meshes, all in the $.ply$ format, see Figure \ref{fig:objects}. Note that the modelling setup is not radiometrical calibrated.

@@

\subsection{Scene scanning}\label{sec:scene_scanning}
For the data collection we use a 6-axis ABB IRB 1600 industrial robot to provide a precise and highly repeatable camera pose. The robot is equipped with two PointGray Grasshopper3 GS3-U391S6C-C USB3 color cameras with resolution of 9.1 Mp and a Wintech Pro4500 projector with a resolution of 1140x912 pixels. The sensor cluster with the structured light sensor (SL) is mounted in the robot tool. 

@@

%\begin{figure}[ht]
%\centering
%\includegraphics[width=0.9\linewidth, height= 0.6\linewidth]{Robot.pdf}
%\caption{Scan of the full scene with view frames}
%\label{fig:robot}
%\end{figure}

@@

\includegraphics[clip, trim=14cm 6cm 13cm 8cm,width=1.0\linewidth, height= 1.0\linewidth, keepaspectratio]{img/mesh_scene.png}

@@

\subsection{Ground Truth 6D pose}\label{sec:gt_pose}

@@

\subsection{Pose estimation}\label{sec:pose_estimation}

@@

In this section we present the results of our evaluation benchmark. All experiments are based on the proposed dataset where 3204 scenes, 45 objects and 5675 ground truth poses are included. As a first evaluation we benchmark the matching accuracy of the seven feature descriptors with the parameters outlined in Section \ref{sec:benchmark_matching} and all 45 object models included. The PRC curve of the overall matching accuracy is presented in Figure \ref{fig:all_L2_RATIO_zoom}.   

@@

As expected the total matching accuracy is much lower compared to previous studies e.g. Guo \etal \cite{Guo2015} and Buch \etal \cite{Buch2016}, which both are running a similar benchmark but on previous proposed datasets. The result indicate that our objective of the proposed dataset has been fulfilled. Moreover, the evaluation shows that the ECSAD feature has a best performance with a AUC = 0.046 followed by ROPS with AUC = 0.011. In order to investigate the performance further we run the matching benchmark for each object model and compute PRC curves for each of the 45 models. We have categorize the object into three different groups and present 3 PRC curves for each group in Figure \ref{fig:angel}-\ref{fig:noise} as a sample. The three groups are a) Geometric complex objects, b) Cylindrical objects and c) Flat or box shaped objects. The objects that corresponds to the PRC curves in Figure \ref{fig:angel}-\ref{fig:noise} are presented in Figure \ref{fig:selected_objects}. The geometric complex objects are the Angel, the Birds and the Rabbit in Figure \ref{fig:selected_objects}(a)-(c), the cylindrical objects are Neutral, Pringles and Hand soap in Figure \ref{fig:selected_objects}(d)-(f), and the flat or box shaped objects are the button, the brake disc and the Psu in Figure \ref{fig:selected_objects}(g)-(i). The results show that a recent precision and recall are achieved with the Angel,Birds and Rabbit, but it is much lower than previous studies e.g. Buch \etal \cite{Buch2016} that obtain very matching accuracy for some datasets. These low numbers for our geometric ideal objects indicate that the proposed dataset have the desired level of complexity.     Regarding, the cylindrical objects which features the Neutral, Pringles and Hand Soap objects, it is clear that current local shape descriptors is very little descriptive for these uniform shaped objects. Again, ECSAD performs in general best which might results from the fact that ECSAD describes edges in a good way. For the flat and boxed shaped models we can conclude that current state of the art feature descriptors is not suitable as the only detection method.\\ 	
\indent The result for the pose estimation experiments are presented in Table \ref{tab:recognition} and Figure \ref{fig:pose_est_results}. Our object recognition pipeline in these experiment is in accordance to the presented pipeline in Section \ref{sec:pose_estimation}. 
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\begin{table*}[t]
\scalebox{0.8}{
\begin{tabular}{p{1.25cm} | P{1.1cm} | P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.4cm} P{1.7cm} P{1.4cm} P{1.65cm} P{1.4cm} | P{1.4cm}}
\textbf{Feature} & \textbf{Overall} & \textbf{Angel} & \textbf{Birds} & \textbf{Rabbit} & \textbf{Neutral} & \textbf{Pringels} & \textbf{Hand soap} & \textbf{Button} & \textbf{Brake Disc} & \textbf{Psu}  & \textbf{\textit{Mean ($\lambda$)}} \\
 \textbf{\textit{ECSAD}}  & 0.21  & \textbf{0.59} & \textbf{0.86} & \textbf{0.62} & 0.00 & 0.06 & 0.03 & 0.00 & 0.00 & 0.00 & 0.00\\
 \textbf{\textit{FPFH}}   & 0.01  & 0.07 & 0.01 & 0.04 & 0.00 & 0.00 & 0.02 & 0.00 & 0.00 & 0.00 & 0.00\\
 \textbf{\textit{NDHIST}} & 0.02  & 0.13 & 0.05 & 0.14 & \textbf{0.02} & \textbf{0.06} & 0.02 & 0.00 & 0.00 & 0.00 & 0.00\\
 \textbf{\textit{ROPS}}   & 0.13  & 0.45 & 0.70 & 0.29 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
 \textbf{\textit{SHOT}}   & 0.04  & 0.25 & 0.09 & 0.14 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
 \textbf{\textit{SI}}     & 0.05  & 0.20 & 0.16 & 0.10 & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
 \textbf{\textit{USC}}    & 0.00  & 0.01 & 0.04 & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
%\textbf{\textit{PFH}}    & 0.00 \vline  & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
%\textbf{\textit{3DSC}}   & 0.00 \vline  & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00\\
}
\caption{Overall recognition rates. \textbf{Column 1:} Features descriptors. \textbf{Column 2:} Overall recognition rate. \textbf{Column 3-11:} Recognition rate for each sample object in Figure \ref{fig:selected_objects}. \textbf{Column 12:} Mean recognition rate for the 9 sample object per. feature.}
\label{tab:recognition}
\end{table*}
\begin{figure*}[t]
	\begin{subfigure}[Ecsad]{%{0.18\textwidth}
		\includegraphics[clip, trim=6.7cm 1cm 6.7cm 3.5cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/ecsad_1.png}
		%\subcaption{Angel}\label{fig:stl_n3}
		}
	\end{subfigure}
	\begin{subfigure}[Ndhist]{%{.18\textwidth}	
		\includegraphics[clip, trim=5cm 1cm 5cm 1cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/ndhist.png}
		%\caption{Birds}\label{fig:stl_n3}
		}
	\end{subfigure}
	\begin{subfigure}[Rops]{%{.18\textwidth}
		\includegraphics[clip, trim=4cm 1cm 7cm 1.7cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/rops.png}
		%\subcaption{Rabbit}\label{fig:stl_n3}
		}
	\end{subfigure}
	\\
	\begin{subfigure}[Shot]{%{.18\textwidth}	
		\includegraphics[clip, trim=6cm 2cm 5cm 0.8cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/shot.png}
		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
		}
	\end{subfigure}
	\begin{subfigure}[Fpfh]{%{.18\textwidth}
		\includegraphics[clip, trim=7.2cm 2cm 7.2cm 3.3cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/fpfh.png}
		%\caption{Noise level 3 for STL dataset}\label{fig:stl_n3}
		}
	\end{subfigure}
	\begin{subfigure}[Spin images]{%{.18\textwidth}
		\includegraphics[clip, trim=4.2cm 2cm 6cm 0.2cm,width=0.3\linewidth, height= 0.2\linewidth, keepaspectratio]{img/si.png}
